---
title: ""
output: html_document
---

```{r setup, include=FALSE}

library(plotly)
library(ggplot2)
library(dplyr)


movie_bechdel = read.csv("movie_bechdel.csv")
```
# Women Empowerment: The Bechdel Test

(https://en.wikipedia.org/wiki/Bechdel_test) The Bechdel test (/ˈbɛkdəl/ BEK-dəl), also known as the Bechdel–Wallace test, is a measure of the representation of women in fiction. It asks whether a work features at least two women who talk to each other about something other than a man. The requirement that the two women must be named is sometimes added.

# Do movies that pass the Bechdel Test get rated more highly?

We want to see whether movies that pass the Bechdel Test are rated more highly than movies that fail the Bechdel test. We examine this for men and for women separately.

## Among Women:

```{r bechdel_female, echo=FALSE}
#plot
movie_bechdel %>%
  filter(gender == "F") %>%
  mutate(passed_bechdel = ifelse(rating_bechdel >= 3, "Passed", "Failed")) %>%
  mutate(rated_4_plus = ifelse(rating_user >= 4, "Yes", "No")) %>%
  ggplot(aes(fill=rated_4_plus, x=passed_bechdel)) + 
  geom_bar(position="fill") +
  ggtitle("Female Users Proportion of Rating 4+ \n by Pass or Fail Bechdel Test") +
  ylab("Proportion") +
  geom_text(aes(label=stat(count)), stat="count", position= 'fill') +
  scale_fill_manual(values = c("#a73c5a", "#ff7954"))
```

### Chi-Square Test

From a chi-square test on the proportion of movies getting a 4+ rating, the p-value is significant, and indicates that the movies that fail the Bechdel Test have a higher proportion of 4+ ratings.

```{r bechdel_female_chi, echo=FALSE}
#chi square test
female_ratings = movie_bechdel %>%
  filter(gender == "F") %>%
  mutate(passed_bechdel = ifelse(rating_bechdel >= 3, "Passed", "Failed")) %>%
  group_by(passed_bechdel) %>%
  summarise(n_ratings_4_plus = sum(rating_user >= 4), n_total = n())

print(female_ratings)
print(paste("Proportion of females that rate >=4 for movies that passed Bechdel:", female_ratings$n_ratings_4_plus[2]/female_ratings$n_total[2]))
print(paste("Proportion of females that rate >=4 for movies that failed Bechdel:", female_ratings$n_ratings_4_plus[1]/female_ratings$n_total[1]))

prop.test(female_ratings$n_ratings_4_plus, female_ratings$n_total)
```

## Among Men:

```{r bechdel_male, echo=FALSE}
#plot
movie_bechdel %>%
  filter(gender == "M") %>%
  mutate(passed_bechdel = ifelse(rating_bechdel >= 3, "Passed", "Failed")) %>%
  mutate(rated_4_plus = ifelse(rating_user >= 4, "Yes", "No")) %>%
  ggplot(aes(fill=rated_4_plus, x=passed_bechdel)) + 
  geom_bar(position="fill") +
  ggtitle("Male Users Proportion of Rating 4+ \n by Pass or Fail Bechdel Test") +
  ylab("Proportion") +
  geom_text(aes(label=stat(count)), stat="count", position= 'fill') +
  scale_fill_manual(values = c("#a73c5a", "#ff7954"))
```

### Chi-Square Test

From a chi-square test on the proportion of movies getting a 4+ rating, the p-value is significant, and indicates that the movies that fail the Bechdel Test have a higher proportion of 4+ ratings.

```{r bechdel_male_chi, echo=FALSE}
#chi square test
male_ratings = movie_bechdel %>%
  filter(gender == "M") %>%
  mutate(passed_bechdel = ifelse(rating_bechdel >= 3, "Passed", "Failed")) %>%
  group_by(passed_bechdel) %>%
  summarise(n_ratings_4_plus = sum(rating_user >= 4), n_total = n())

print(male_ratings)
print(paste("Proportion of males that rate >=4 for movies that passed Bechdel:", male_ratings$n_ratings_4_plus[2]/male_ratings$n_total[2]))
print(paste("Proportion of males that rate >=4 for movies that failed Bechdel:", male_ratings$n_ratings_4_plus[1]/male_ratings$n_total[1]))

prop.test(male_ratings$n_ratings_4_plus, male_ratings$n_total)
```


# Histograms of the Ratings by Male and Female

```{r histograms, echo = FALSE, warning=FALSE, message=FALSE}
passed = movie_bechdel %>%
  filter(rating_bechdel == 3)

failed = movie_bechdel %>%
  filter(rating_bechdel < 3)

passed_male_ratings = passed %>%
  filter(rating_bechdel == 3) %>%
  filter(gender == "M") %>%
  select(rating_user)

passed_female_ratings = passed %>%
  filter(rating_bechdel == 3) %>%
  filter(gender == "F") %>%
  select(rating_user)

passed_male_ratings = passed %>%
  filter(rating_bechdel == 3) %>%
  filter(gender == "M") %>%
  select(rating_user)

passed_female_ratings = passed %>%
  filter(rating_bechdel == 3) %>%
  filter(gender == "F") %>%
  select(rating_user)

#plots
passed %>%
  ggplot( aes(x=rating_user, fill=gender)) +
  geom_histogram(position = 'dodge') +
  ggtitle("Distribution of Ratings by Gender \nfor Movies that Pass the Bechdel Test") +
  scale_fill_manual(values = c("#a73c5a", "#ff7954"))
  
failed %>%
  ggplot( aes(x=rating_user, fill=gender)) +
  geom_histogram(position = 'dodge') +
  ggtitle("Distribution of Ratings by Gender \nfor Movies that Fail the Bechdel Test") +
  scale_fill_manual(values = c("#a73c5a", "#ff7954"))

```



